Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex
An important detail of alg's cost and start to rewrite of the weakest paragraph

  In total, the cost of \TAlg is at most $\TAlg(\sigma_I) + \TAlg(\sigma_E) + \TAlg(M) \leq 10\alpha\cdot \ell + \TAlg(\sigma_E)$ during this phase.

@@

  \medskip
  \maciek{The weakest paragraph}
  \maciek{x must be a sequence of requests, not the number; better name for x}
  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ with respect to $\sigma_E$.
  We begin by lower-bounding the number of requests from $\sigma_E$ that $\OPT$ must account (by either serving remotely or migrating), and we denote their number by $x$.
  It holds that $x \geq \TAlg(\sigma_E) - 3\cdot\ell\cdot(\alpha - 1)$, as it received all the requests that \TAlg did, but it could ignore the cost of serving at most $3\cdot\ell$ pairs of nodes, as it might have them collocated in its clusters.
  Each such pair of nodes account for at most $\alpha-1$ requests (the pairs from $\sigma_E$ are unsaturated) in the cost of $\TAlg(\sigma_E)$, hence collocating them would decrease their number by at most $3\cdot\ell\cdot(\alpha - 1)$.

>>>>

  Moreover, \TAlg paid for all requests from $\sigma_E$, and we bound it $\TAlg(\sigma_E) = |\sigma_E|$.
  In total, the cost of \TAlg is at most $\TAlg(\sigma_I) + \TAlg(\sigma_E) + \TAlg(M) \leq 10\alpha\cdot \ell + |\sigma_E|$ during this phase.

@@

  \medskip
  \maciek{The weakest paragraph}
  \maciek{x must be a sequence of requests, not the number; better name for x}
  Before we bound the competitive ratio, we relate the costs of $\TAlg$ and $\OPT$ with respect to requests $\sigma_E$.

  In a fixed configuration of $\OPT$, it might mitigate paying for requests between at most $3\ell$ pairs of nodes by collocating them in its clusters.
  Recall that $\sigma_E$ consist of requests between unsaturated pairs, and it accounts only for requests that increased the counter (i.e., external requests), thus $\OPT$ might mitigate at most $3\ell\cdot(\alpha - 1)$ requests from $\sigma_E$.
  Faced with

  We begin by lower-bounding the number of requests from $\sigma_E$ that would incur a cost for $\OPT$ if it .

  may  account (by either serving remotely or migrating), and we denote their number by $x$.
  It holds that $x \geq \TAlg(\sigma_E) - 3\cdot\ell\cdot(\alpha - 1)$, as it received all the requests that \TAlg did, but it could ignore the cost of serving at most $3\cdot\ell$ pairs of nodes, as it might have them collocated in its clusters.
  Each such pair of nodes account for at most $\alpha-1$ requests (the pairs from $\sigma_E$ are unsaturated) in the cost of $\TAlg(\sigma_E)$, hence collocating them would decrease their number by at most $3\cdot\ell\cdot(\alpha - 1)$.
